```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(arrow)
library(lsr)
library(rcompanion)
library(scales)
library(patchwork)
library(effectsize)
library(effsize)
library(GGally)
```


# Load corpus with precomputed stigma scores 
```{r}
corpus <- read_parquet("../data/data_with_stigmascores.parquet") |> 
    filter(id_subcorpus == "psyC" | id_subcorpus == "psyB")
```


# Load processed active learning predictions
```{r}
depression_predictions <- read_csv("../data/active_learning/predictions/1105_predictions_depression_processed.csv") |> 
    select(-1)
schizophrenia_predictions <- read_csv("../data/active_learning/predictions/1105_predictions_schizophrenia_processed.csv") |> 
    select(-1)
```


# Join predictions on corpus
```{r}
corpus_depression <- corpus |> 
    left_join(depression_predictions, by = c("id" = "id")) |> 
    filter(!is.na(predicted_class)) # filter out snippets that were not included in the active learning process (i.e., those with NA predictions)

depression_combined <- bind_rows(
    corpus_depression |>  mutate(group = "Unfiltered"),
    corpus_depression |>  filter(predicted_class == 1) |>  mutate(group = "Medical"),
    corpus_depression |>  filter(predicted_class == 0) |>  mutate(group = "Non-Medical")
) |> 
    mutate(
        group = as_factor(group)
    )

corpus_schizophrenia <- corpus |> 
    left_join(schizophrenia_predictions, by = c("id" = "id")) |> 
    filter(!is.na(predicted_class))

schizophrenia_combined <- bind_rows(
    corpus_schizophrenia |>  mutate(group = "Unfiltered"),
    corpus_schizophrenia |>  filter(predicted_class == 1) |>  mutate(group = "Medical"),
    corpus_schizophrenia |>  filter(predicted_class == 0) |>  mutate(group = "Non-Medical")
)

```

# Get examples with highest confidence for each disease to showcase
```{r}

# Depression non-medical
dep_nonmedical <- depression_combined |> 
    filter(group == "Non-Medical") |> 
    arrange(desc(prob_class_zero)) |> 
    slice_head(n = 5) |> 
    pull(text)

dep_nonmedical

# Schizophrenia non-medical
schiz_nonmedical <- schizophrenia_combined |> 
    filter(group == "Non-Medical") |> 
    arrange(desc(prob_class_zero)) |> 
    slice_head(n = 5) |> 
    pull(text)

schiz_nonmedical

```


# Plot the label distribution of the classifier predictions for both diseases
```{r}

depression_predictions |> 
    group_by(predicted_class) |> 
    summarise(
        n = n()
    ) |> 
    mutate(
        percent = n / sum(n) * 100,
        label = case_when(
            predicted_class == 0 ~ "Non-Medical",
            predicted_class == 1 ~ "Medical"
        )
    ) |> 
    ggplot(aes(x = label, y = percent, fill = label)) +
    geom_bar(stat = "identity", color = "black", alpha = 0.7) +
    labs(
        title = "Depression: Distribution of Predicted Labels",
        x = "Predicted Label",
        y = "Percentage (%)"
    ) +
    theme_minimal() +
    theme(
        legend.position = "none",
        text = element_text(size = 9),
        axis.text.x = element_text(color = "black", size = 9),
        axis.text.y = element_text(color = "black", size = 9)
    ) +
    scale_fill_brewer(palette = "Set1") +
    scale_y_continuous(labels = label_number(scale_cut = cut_short_scale())) -> dep_label_dist_plot

dep_label_dist_plot


schizophrenia_predictions |> 
    group_by(predicted_class) |> 
    summarise(
        n = n()
    ) |> 
    mutate(
        percent = n / sum(n) * 100,
        label = case_when(
            predicted_class == 0 ~ "Non-Medical",
            predicted_class == 1 ~ "Medical"
        )
    ) |> 
    ggplot(aes(x = label, y = percent, fill = label)) +
    geom_bar(stat = "identity", color = "black", alpha = 0.7) +
    labs(
        title = "Schizophrenia: Distribution of Predicted Labels",
        x = "Predicted Label",
        y = "Percentage (%)"
    ) +
    theme_minimal() +
    theme(
        legend.position = "none",
        text = element_text(size = 9),
        axis.text.x = element_text(color = "black", size = 9),
        axis.text.y = element_text(color = "black", size = 9)
    ) +
    scale_fill_brewer(palette = "Set1") +
    scale_y_continuous(labels = label_number(scale_cut = cut_short_scale())) -> dep_label_dist_plot

dep_label_dist_plot

```


# Distribution Plots
These plots show Kernel-Density Estimates for the distribution of stigma scores for the three groups (Unfiltered, Medical, Non-Medical) for both diseases.
```{r}
schizophrenia_combined |> 
    mutate(
        group = factor(group, levels = c("Non-Medical", "Unfiltered", "Medical"))
    ) |> 
    ggplot(aes(x = stigma_score, color = group, fill = group)) +
    geom_density(alpha = 0.5) +
    labs(
        title = "Schizophrenia",
        x = "Stigma Score",
         y = "Density",
         fill = "Included Snippets",
         color = "Included Snippets"
        ) +
    theme_classic() +
    theme(
        legend.position = "bottom",
        plot.title = element_text(size = 10),
        text = element_text(size = 9),
        legend.title = element_blank(),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.8,"line"),
        axis.text.x = element_text(color = "black", size = 9),
        axis.text.y = element_text(color = "black", size = 9)
        ) +
    scale_fill_manual(values = c("grey", "#377EB8", "red")) +
    scale_color_manual(values = c("grey", "#377EB8", "red")) -> schiz_kde_plot

schiz_kde_plot

#ggsave("schiz_kde_plot.pdf", plot = schiz_kde_plot, width = 3.25, height = 2.75, dpi = 300)

depression_combined |> 
    mutate(
        group = factor(group, levels = c("Non-Medical", "Unfiltered", "Medical"))
    ) |> 
    ggplot(aes(x = stigma_score, fill = group, color = group)) +
    geom_density(alpha = 0.5) +
    labs(x = "Stigma Score",
         title = "Depression",
         y = "Density",
         fill = "Included Snippets",
         color = "Included Snippets") +
    theme_classic(
        #base_family = "Times New Roman"
    ) +
    theme(
        legend.position = "bottom",
        text = element_text(size = 9),
        plot.title = element_text(size = 10),
        legend.title = element_blank(),
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.8,"line"),
        axis.text.x = element_text(color = "black", size = 9),
        axis.text.y = element_text(color = "black", size = 9),
        panel.grid.major = element_blank(),  # darker major grid lines
        panel.grid.minor = element_blank(),  # lighter minor grid lines
        panel.background = element_rect(fill = "white")
        ) +
    scale_fill_manual(values = c("grey", "#377EB8", "red")) +
    scale_color_manual(values = c("grey", "#377EB8", "red")) +
    guides(fill = guide_legend(override.aes = list(size = 2)))-> dep_kde_plot

dep_kde_plot

#ggsave("dep_kde_plot.pdf", plot = dep_kde_plot, width = 3.25, height = 2.75, dpi = 300)

```
# Cohen's d Effect Sizes
```{r}
schiz_distribution_table <- schizophrenia_combined |> 
    group_by(group) |> 
    summarise(
        mean = mean(stigma_score),
        sd = sd(stigma_score),
        n = n(),
        percent = n() / nrow(filter(schizophrenia_combined, group == "Unfiltered")) * 100
    )

dep_distribution_table <- depression_combined |> 
    group_by(group) |> 
    summarise(
        mean = mean(stigma_score),
        sd = sd(stigma_score),
        n = n(),
        percent = n() / nrow(filter(depression_combined, group == "Unfiltered")) * 100
    )


distribution_table <- bind_rows(
    schiz_distribution_table |> mutate(disease = "Schizophrenia"),
    dep_distribution_table |> mutate(disease = "Depression")
) |> 
    mutate(
        disease = as_factor(disease),
        group = as_factor(group)
    )
```


# Pairwise comparisons of effect sizes
```{r}
cohen_d_list <- list(
    depression_medical_all <- cohens_d(
      x = filter(depression_combined, group == "Medical")$stigma_score,
      y = filter(depression_combined, group == "Unfiltered")$stigma_score,
      method = "pooled"
    ),
    
    schizophrenia_medical_all <- cohens_d(
      x = filter(schizophrenia_combined, group == "Medical")$stigma_score,
      y = filter(schizophrenia_combined, group == "Unfiltered")$stigma_score,
      method = "pooled"
    ),
    
    schizophrenia_all_depression_all <- cohens_d(
      x = filter(schizophrenia_combined, group == "Unfiltered")$stigma_score,
      y = filter(depression_combined, group == "Unfiltered")$stigma_score,
      method = "pooled"
    ),

    schizophrenia_medical_depression_medical <- cohens_d(
      x = filter(schizophrenia_combined, group == "Medical")$stigma_score,
      y = filter(depression_combined, group == "Medical")$stigma_score,
      method = "pooled"
    )
)


cohen_d_df <- cohen_d_list |> 
    enframe() |> 
    unnest_wider("value") |> 
    mutate(
        disease = c("depression", "schizophrenia", "both", "both"),
        comparison = c(
            "Depression\n (Unfiltered vs Medical)", 
            "Schizophrenia\n (Unfiltered vs Medical)", 
            "Schizophrenia vs\n Depression (Unfiltered)", 
            "Schizophrenia vs\n Depression (Medical)"
            )
    ) |> 
    mutate(
        comparison = factor(comparison, levels = rev(unique(comparison)))
    )

ggplot(cohen_d_df, aes(x = comparison, y = Cohens_d, color = disease)) +
    geom_point(size = 3, shape = 15) +
    geom_linerange(aes(ymin = CI_low, ymax = CI_high)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    coord_flip() +
    labs(y = "Cohen's d", x = "") +
    theme_minimal() +
    scale_color_manual(values = c("depression" = "#377EB8", "schizophrenia" = "#E41A1C", "both" = "#4DAF4A")) +
    scale_y_continuous(limits = c(0, 0.7)) +
    theme(
        text = element_text(size = 9, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size = 0.05, color = "grey40"),
        panel.grid.minor = element_line(size = 0.05, color = "grey40"),
        panel.background = element_rect(fill = "white"),
        legend.background = element_rect(fill = "white", color = "black", linewidth = 0.4),
        axis.text.x = element_text(color = "black", size = 10),
        axis.text.y = element_text(color = "black", size = 7)
    ) +
    guides(size = "none") -> cohen_d_plot

cohen_d_plot

#ggsave("effect_sizes_cohen.pdf", plot = cohen_d_plot, width = 3.25, height = 2.75, units = "in", dpi = 300)
```

# Visualise Results of the Hyperparameter Optimisation Analysis
```{r}

schiz_study <- read_csv("../data/1005_schiz_study.csv") |> 
    select(-1, -8) |> 
    rename(f1 = value,
           batch_size = params_batch_size,
           learning_rate = params_body_learning_rate,
           max_steps = params_max_steps,
           num_iterations = params_num_iterations) |> 
    mutate(
        f1_dup = case_when(
            f1 > 0.8 ~ "high",
            f1 > 0.75 ~ "mid",
            .default = "low"
        ) |> 
            as_factor()
    )

dep_study <- read_csv("../data/1005_dep_study.csv") |> 
    select(-1, -8) |> 
    rename(f1 = value,
           batch_size = params_batch_size,
           learning_rate = params_body_learning_rate,
           max_steps = params_max_steps,
           num_iterations = params_num_iterations) |> 
    mutate(
        f1_dup = case_when(
            f1 > 0.8 ~ "high",
            f1 > 0.75 ~ "mid",
            .default = "low"
        ) |> 
            as_factor()
    )


schiz_best_row <- schiz_study |> 
  filter(f1 == max(f1))

ggparcoord(
  data = schiz_study,
  columns = 2:6,
  order = c(2,3,4,5,6),
  groupColumn = 7,
  scale = "uniminmax",
  showPoints = F,
  alphaLines = 0.7
  ) +
  scale_color_manual(
    values = c("low" = "grey70", "mid" = "orange", "high" = "red")
  ) +
  scale_size(range = c(0.1, 1)) +
  labs(
    title = "Schizophrenia",
    y = "Normalized Values",
    color = "F1-score",
    size = "F1-score"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
    plot.title = element_text(size = 10),
    axis.text.y = element_text(color = "black"),
    text = element_text(size = 10),
    axis.title.y = element_text(size = 9, color = "black"),
    axis.title.x = element_blank(),
    legend.key.size = unit(0.5, "cm"),
    legend.position = "bottom",
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(size = 0.05, color = "grey80"), 
    panel.grid.minor = element_line(size = 0.05, color = "grey80")
    ) -> schiz_hpo_plot

schiz_hpo_plot


#ggsave("hpo_schizophrenia.pdf", plot = schiz_hpo_plot, width = 3.25, height = 2.75, units = "in", dpi = 300)

ggparcoord(
  data = dep_study,
  columns = 2:6,
  order = c(2,3,4,5,6),
  groupColumn = 7,
  scale = "uniminmax",
  scaleSummary = "robust",
  showPoints = F,
  alphaLines = 0.7
) +
  scale_color_manual(
    values = c("low" = "grey70", "mid" = "orange", "high" = "red")
  ) +
  labs(
    title = "Depression",
    y = "Normalized Values",
    size = "F1-score",
    color = "F1-score"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 10),
    axis.text.x = element_text(angle = 45, hjust = 1, color = "black"),
    axis.text.y = element_text(color = "black"),
    text = element_text(size = 10),
    axis.title.y = element_text(size = 9, color = "black"),
    axis.title.x = element_blank(),
    legend.key.size = unit(0.5, "cm"),
    legend.position = "bottom",
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(size = 0.05, color = "grey80"),
    panel.grid.minor = element_line(size = 0.05, color = "grey80")
    ) -> dep_hpo_plot

dep_hpo_plot

#ggsave("hpo_depression.pdf", plot = dep_hpo_plot, width = 3.25, height = 2.75, units = "in", dpi = 300)
```

